\documentclass{article}
\usepackage{graphicx}
\usepackage[margin=0.5in]{geometry}
\title{Lost Mine of Phandelver Notes}
\date{2024}
\begin{document}
\maketitle
\section{Sildar Holwinter}
A friend of Gundred, was with him when they were ambushed by the goblins. Sildar says Gundred was taken to a "Kragmor Castle."
\section{Phandalin}
The owners of the \emph{Stonehill Inn,} Toblen and Trilena Stonehill say that because of the Orks to the east and the Red Brands gang; Business is poor.

\emph{Rumors} overheard throughout town:
Someone poking around at the old owl well (50 miles NE)?
Something mysterious about the old adventurer of the orchard.

\emph{Harbin Wester} the townmaster is reluctant to do his job, and does not want to help Sildar in setting up the Lord's alience in Phandalin. Perhaps fixing the issues of the gang and orks could convince him?

A lady at the \emph{Miner's Excahnge} takes a loot at out gem; she says it is faintly magical and very well cut. Glastaf is hanging around the old manour, apparently she saw someone being dragged there.

The \emph{Shrine of Luck} is dedicated to Tmoir, the god of luck and good fortune. Sister Garaele says she is responsible for the shrine, a place where people come to pry for good fortune. A couple of people have ended up dead in the middle of the street; A farmer, a miner, and now one of the Red Brands who's corpse is in the shrine itself.

Bounties:
	Red Brands: 100GP
	Orks: lots
	Glastaf: 100GP (50 upfront, 50 after)
\end{document}